Distance Sampling in \proglang{R}

### 2016-01-05 paper.Rmd
Added paragraphs about mads and DSsim
Added paragraphs about mads and DSsim to Extensions section

>>>>

Further distance sampling complexities such as uncertainty in measured covariates (e.g. cluster size) and model uncertainty (when two models have similar fit but substantially different estimates) can be incorporated using the multi-analysis distance sampling package \pkg{mads} [@mads-pkg]. In addition, \pkg{mads} can also incorporate sightings for which species identification could not be achieved. This is done by estimating the abundance of these 'unidentified' sightings and pro-rating them as described in [@Gerrodette:2005].

In addition to the analyses, an equally if not more important stage of a distance sampling survey is the survey design. We have therefore developed a package which allows users to test out different designs in their specific study region and tailor population attributes to reflect the species they are working with. In this way \pkg{DSsim} [@DSsim-pkg] allows users to more easily identify challenges unique to their study and select a survey design which is likely to yield the most accurate and precise results.
